\documentclass[12pt,epsf]{report}
\usepackage[dvips]{graphicx}
\usepackage{tabularx}
\usepackage{latexsym}
\usepackage{e_ics}
\usepackage{verbatim}
\usepackage{moreverb}
\usepackage{makeidx}

\newtheorem{definition}{定義}[chapter]
\newtheorem{algorithm}{アルゴリズム}[chapter]

%% end of local definitions

\def\epsfsize#1#2{\ifnum#1>\hsize\hsize\else#1\fi}

%% make index
\makeindex

\begin{document}

\papercode{ICS-**M-***}
\title{English Title}
\jtitle{日本語タイトル}
\major{理工学研究科 数理電子情報系専攻}
\course{情報システム工学コース}
\author{著者名}
\date{平成21年2月5日提出}
\supervisor{＊ ＊＊ 教授}
\labname{＊＊＊＊研究室}
\studentID{0XMM000}
\maketitle

%\setlength{\baselineskip}{1.5\baselineskip} %double space

\pagenumbering{roman}
%\setcounter{page}{1}
\begin{abstract}
\addcontentsline{toc}{chapter}{Abstract}
%\pagestyle{empty}
Here is abstract.
\end{abstract}


% ################## 謝辞 ##################
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\setcounter{page}{2}
\noindent
Here is acknowledgements.

\tableofcontents
\listoffigures
\addcontentsline{toc}{chapter}{List of figures}
\listoftables
\addcontentsline{toc}{chapter}{List of tables}


\chapter{Introduction}
\pagenumbering{arabic}
\setcounter{page}{1}


\section{Background}

Background

\section{Purpose and Objective}

Purpose and Objective

\section{Construction}
The rest of thesis organised as follows:
Chapter Y explains ... 
Chapter Z gives conclusion and future works.


\chapter{Hogehoge}

hahahahah.

\chapter{Fugafuga}
\section{Foofoo}
hehehehe

\section{Hyohyo}

fufufufufufufu.

\chapter{Conclusion}
\section{Summary}

We have ...

\section{Future Works}

Future works are as follows: ...

\newpage

\chapter*{Publications}
\addcontentsline{toc}{chapter}{Publications}

\begin{list}%
 {} %default label
 {} %formatting parameter
 \item Refereed papers published in journals or books (first author)
       \begin{itemize}
	\item Hogehoge: ....
       \end{itemize}
 \item Refereed papers published in journals or books (co-author)
       \begin{itemize}
	\item Hogehoge: ....
       \end{itemize}
 \item Refereed papers published in international conference proceedings (first author)       \begin{itemize}
	\item Hogehoge: ....
       \end{itemize}

 \item Refereed papers published in international conference proceedings (co-author)
       \begin{itemize}
	\item Hogehoge: ....
       \end{itemize}
 \item Refereed papers published in local conference proceedings (first author)
       \begin{itemize}
	\item Hogehoge: ....
       \end{itemize}
 \item Refereed papers published in local conference proceedings (co-author)
       \begin{itemize}
	\item Hogehoge: ....
       \end{itemize}
\end{list}

%\bibliographystyle{aiseplain}
%\bibliography{ref}
\begin{thebibliography}{99}
\label{sannkoubunnkenn_chapter}

\bibitem{Goto01}
Yuichi GOTO, Daisuke TAKAHASHI, and Jingde CHENG: Parallel Forward
        Deduction Algorithms of General-Purpose Entailment Calculus on
        Shared-Memory Parallel Computers, Proceedings of the ACIS 2nd
        International Conference on Software Engineering, Artificial
        Intelligence, Networking \& Parallel/Distributed Computing,
        pp. 168-175, Nagoya, Japan, August 2001.

\end{thebibliography}


\renewcommand{\thesection}{\Alph{section}}
\appendix
\addcontentsline{toc}{chapter}{Appendix}
\chapter{Huroku}

kokokokoo.

\chapter{MataHuroku}

kokokokoko.

%\printindex
%\addcontentsline{toc}{chapter}{Index}
%目次にIndexを表示させる場合は.idxファイルのtheindex環境の中で
%上記コマンドを置く
\end{document}
